Well Hello There!

### 2025-08-05 index.qmd
Update with proper downloads
Resume Update

Hello there! My name is Marzuki Nooranas \[[Resume](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)\] - or *Marz* for short! I am currently in my 3rd year, majoring in Sociology and Interactive Media Development!

>>>>

Hello there! My name is Marzuki Nooranas or *Marz* for short! I am currently in my final year, majoring in Sociology and Interactive Media Development!
